The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-01-11 paper/draft.tex
typo

One of the first and to this day haighly influential formal theories of island biodiversity is MacArthur and Wilson's seminal equilibrium theory of island biogeography (ETIB). %TODO: ref
In it, species richness on islands is the result of opposing rates of immigration and extinction, both of which in turn are modified by island size (area) and its distance from the mainland (isolation).
This relationship was since successfully applied to a multitude of islands %TODO: refs
, but also island like systems, such as coral reefs, lakes/ponds or forest fragments. %TODO: refs
This general applicability, however, can not hide the fact that the ETIB fails to deliver a mechanistic explanation of the processes at play.
It has particularly been criticized for its lack of considering speciation. %TODO: refs

>>>>

One of the first and to this day highly influential formal theories of island biodiversity is MacArthur and Wilson's seminal equilibrium theory of island biogeography (ETIB). %TODO: ref
In it, species richness on islands is the result of opposing rates of immigration and extinction, both of which in turn are modified by island size (area) and its distance from the mainland (isolation).
This relationship was since successfully applied to a multitude of islands %TODO: refs
, but also island like systems, such as coral reefs, lakes/ponds or forest fragments. %TODO: refs
This general applicability, however, cannot hide the fact that the ETIB fails to deliver a mechanistic explanation of the processes at play.
It has particularly been criticized for its lack of considering speciation. %TODO: refs
